Summary of tumor cell classification with `AUCell` for `r params$library_id`

### 2024-07-11 analyses/cell-type-ewings/template_notebooks/auc-workflow/01-auc-results.Rmd
account for no marker gene expression

---
title: "Summary of tumor cell classification with `AUCell` for `r params$library_id`"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  library_id: NULL
  sce_file: NULL
  aucell_results_file: NULL
  ref_auc_results: NULL
  geneset_scores_file: NULL
  marker_genes_file: NULL
  auc_threshold: NULL
---

@@

# get marker gene expression 
markers_df <- create_marker_gene_df(
  sce,
  classification_df, 
  params$marker_genes_file
)
```

@@

```{r}
# create a density plot showing the distribution of marker gene expression across classification methods 
markers_df |> 
  dplyr::select(barcodes, sum_raw_exp, auc_classification) |> 
  dplyr::distinct() |> 
  ggplot(aes(x = sum_raw_exp, color = auc_classification)) +
  geom_density() +
  scale_color_manual(values = plot_colors) +
  labs(
    x = "Raw sum of marker gene logcounts",
    color = "AUCell classification"
  )
```

@@

```{r}
# plot heatmap of marker genes 
plot_gene_heatmap(marker_gene_matrix, 
                  row_title = "Marker gene symbol",
                  legend_title = "Marker gene \nexpression",
                  annotation = annotation)
```

>>>>

---
title: "Summary of tumor cell classification with `AUCell` for `r params$library_id`"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  library_id: SCPCS000490
  sce_file: "../../../../data/current/SCPCP000015/SCPCS000490/SCPCL000822_processed.rds"
  aucell_results_file: "../../results/aucell_annotation_test/SCPCS000490/SCPCL000822_auc-classifications.tsv"
  ref_auc_results: "../../results/aucell_annotation_test/SCPCS000490/SCPCL000822_auc-classifications.tsv"
  geneset_scores_file: "../../results/aucell_annotation_test/SCPCS000490/SCPCL000822_gene-set-scores.tsv"
  marker_genes_file: "../../references/tumor-marker-genes.tsv"
  auc_threshold: 0.009131468
---

@@

# get marker gene expression 
markers_df <- create_marker_gene_df(
  sce,
  classification_df, 
  params$marker_genes_file
)

# test if _any_ marker genes have expression
if(sum(markers_df$gene_expression) == 0){
  has_marker_gene_exp <- FALSE
  message("No marker gene expression detected, so all plots of marker genes will be skipped.")
} else {
  has_marker_gene_exp <- TRUE
}
```

@@

```{r, eval=has_marker_gene_exp}
# create a density plot showing the distribution of marker gene expression across classification methods 
markers_df |> 
  dplyr::select(barcodes, sum_raw_exp, auc_classification) |> 
  dplyr::distinct() |> 
  ggplot(aes(x = sum_raw_exp, color = auc_classification)) +
  geom_density() +
  scale_color_manual(values = plot_colors) +
  labs(
    x = "Raw sum of marker gene logcounts",
    color = "AUCell classification"
  )
```

@@

```{r, eval=has_marker_gene_exp}
# plot heatmap of marker genes 
plot_gene_heatmap(marker_gene_matrix, 
                  row_title = "Marker gene symbol",
                  legend_title = "Marker gene \nexpression",
                  annotation = annotation)
```
